Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-06 doc/main_jfm.tex
adding some texts

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{float}

@@

@@

The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_0.eps}
\includegraphics[width=0.3\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
  }
    \label{figure2}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.4\textwidth]{ReducedArea.eps}
\end{center} 
  \caption{Reduced area transitions over time. The slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure3}
\end{figure}

@@

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.4\textwidth]{N58_rupt_0.eps}
\includegraphics[width=0.4\textwidth]{N58_rupt_200.eps}\\
\includegraphics[width=0.4\textwidth]{N58_rupt_400.eps}
\includegraphics[width=0.4\textwidth]{N58_rupt_600.eps}
\end{center}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure4}
\end{figure}

@@

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
\end{center}
  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under: 
  (b)-(d) extensional flow and (e)-(h) shear flow. 
  }
    \label{figure5}
\end{figure}

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_0.eps}
\includegraphics[width=0.3\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
  }
    \label{figure2}
\end{figure}
%

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{ReducedArea.eps}
\end{center} 
  \caption{Reduced area transitions over time. The slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure3}
\end{figure}
%

@@

The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates. The reduced area is given by $A^* = 4\pi A/L^2$
where $A$ is the vesicle area and $L$ is the arc length of the vesicle.

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.22\textwidth]{N58_rupt_0.eps}
\includegraphics[width=0.22\textwidth]{N58_rupt_200.eps}
\includegraphics[width=0.22\textwidth]{N58_rupt_400.eps}
\includegraphics[width=0.22\textwidth]{N58_rupt_600.eps}
\end{center}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure4}
\end{figure}
%

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
\end{center}
  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under: 
  (b)-(d) extensional flow and (e)-(h) shear flow. 
  }
    \label{figure5}
\end{figure}

@@

\subsection{Vesicle in a Parabolic Flow}

The background flow for this set of simulations is given by

\begin{equation}
{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{10R_0}\right)^2 \right]{\bf e}_x,
\end{equation}
%
where $v_{max}$ is the flow strength. $R_0$ is defined as the radius of the initial vesicle midplane.

\begin{figure}
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
\end{center}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$: 
The configuration is the state when $t=20000$.
  }
    \label{figure6}
\end{figure}
